The Calculus of Linear Constructions

### 2021-10-14 writing/draft2.tex
draft

\renewcommand{\syntleft}{}
\renewcommand{\syntright}{}
\setlength{\grammarparsep}{10pt}
\setlength{\grammarindent}{10em}
\newcommand{\indalt}[1][2]{\\\hspace*{-1.2em}\textbar\quad}
\newcommand{\rname}[1]{\textsc{\footnotesize #1}}
\newcommand{\LNLD}{\text{LNL}_\text{D}}
\newcommand{\ok}{\textbf{ok}}
\newcommand{\pure}[1]{|#1|}
\newcommand{\sort}{\textbf{sort}}
\newcommand{\type}{\textbf{type}}
\newcommand{\refl}{\text{refl}}
\newcommand{\letin}[3]{$\text{let }#1\text{ := }#2\text{ in }#3$}
\newcommand{\new}{\text{new}}
\newcommand{\free}{\text{free}}
\newcommand{\get}{\text{get}}
\newcommand{\set}{\text{set}}
\newcommand{\subst}{\text{subst}}
\newcommand{\utype}{:_{\scriptscriptstyle U}}
\newcommand{\ltype}{:_{\scriptscriptstyle L}}
\newcommand{\stype}[1]{:_#1}
\newcommand{\step}{\leadsto}
\newcommand{\pstep}{\leadsto}
\newcommand{\mrg}[3]{#1\ddagger#2\ddagger#3}
\newcommand{\arw}[2]
{\hspace*{0.2em}{\scriptstyle #1}\hspace*{-0.2em}
\rightarrow
\hspace*{-0.2em}{\scriptstyle #2}\hspace*{0.2em}}
\newcommand{\erase}[1]{\llbracket #1 \rrbracket}

@@

  \subsection{Equality and Parallel Reduction} \label{reduction}
  The operational semantics, and definitional equality of CLC is defined by parallel reductions \cite{takahashi} as presented in Figure \ref{parallel}, all of which are entirely standard.
  \begin{figure}[H]
    \caption{Equality and Parallel Reduction}
    \begin{mathpar}
      \inferrule
      { m_1 \pstep^* n \\ m_2 \pstep^* n }
      { m_1 \equiv m_2 : A }
      \rname{Join}

      \inferrule
      { }
      { x \pstep x }
      \rname{P-Var}

      \inferrule
      { }
      { U \pstep U }
      \rname{P-U}

      \inferrule
      { }
      { L \pstep L }
      \rname{P-L}

      \inferrule
      { n \pstep n' }
      { \lambda x.n \pstep \lambda x.n' }
      \rname{P-$\lambda$}

      \inferrule
      { m \pstep m' \\ n \pstep n' }
      { m\ n \pstep m'\ n' }
      \rname{P-App}

      \inferrule
      { m \pstep m' \\ n \pstep n' }
      { (\lambda x.m)\ n \pstep m'[n'/x] }
      \rname{P-$\beta$}

      \inferrule
      { A \pstep A' \\ B \pstep B' }
      { (x : A) \arw{s}{t} B \pstep (x : A') \arw{s}{t} B' }
      \rname{P-Prod}
    \end{mathpar}
    \label{parallel}
  \end{figure}
  As we have discussed previously, the elimination of the explicit ! exponential allows CLC to maintain a simple operational semantics, whose $\beta$-reductions are very well behaved.

@@

  \begin{lemma} Parallel reduction satisfies the diamond property. \\
    If $m \pstep m_1$ and $m \pstep m_2$ then there exists $m'$ such that $m_1 \pstep m'$ and $m_2 \pstep m'$.
  \end{lemma}

  \begin{corollary} The transitive reflexive closure of parallel reduction is confluent. \\ 
    If $m \pstep^* m_1$ and $m \pstep^* m_2$ then there exists $m'$ such that $m_1 \pstep^* m'$ and $m_2 \pstep^* m'$.
  \end{corollary}

@@

  \begin{lemma} Weakening. \\
    If $\Gamma \vdash m \stype{s} A$ is a valid, then for any $x \notin \Gamma$, judgment $\Gamma, x \utype B \vdash m \stype{s} A$ is derivable.
  \end{lemma}

>>>>

\renewcommand{\syntleft}{}
\renewcommand{\syntright}{}
\setlength{\grammarparsep}{10pt}
\setlength{\grammarindent}{10em}
\newcommand{\indalt}[1][2]{\\\hspace*{-1.2em}\textbar\quad}
\newcommand{\rname}[1]{\textsc{\footnotesize #1}}
\newcommand{\LNLD}{\text{LNL}_\text{D}}
\newcommand{\ok}{\textbf{ok}}
\newcommand{\pure}[1]{|#1|}
\newcommand{\sort}{\textbf{sort}}
\newcommand{\type}{\textbf{type}}
\newcommand{\refl}{\text{refl}}
\newcommand{\letin}[3]{$\text{let }#1\text{ := }#2\text{ in }#3$}
\newcommand{\new}{\text{new}}
\newcommand{\free}{\text{free}}
\newcommand{\get}{\text{get}}
\newcommand{\set}{\text{set}}
\newcommand{\subst}{\text{subst}}
\newcommand{\utype}{:_{\scriptscriptstyle U}}
\newcommand{\ltype}{:_{\scriptscriptstyle L}}
\newcommand{\stype}[1]{:_#1}
\newcommand{\step}{\leadsto}
\newcommand{\pstep}{\leadsto}
\newcommand{\mrg}[3]{#1\ddagger#2\ddagger#3}
\newcommand{\arw}[2]
{\hspace*{0.2em}{\scriptstyle #1}\hspace*{-0.2em}
\rightarrow
\hspace*{-0.2em}{\scriptstyle #2}\hspace*{0.2em}}
\newcommand{\lrw}[2]
{\hspace*{0.2em}{\scriptstyle #1}\hspace*{-0.2em}
\multimap
\hspace*{-0.2em}{\scriptstyle #2}\hspace*{0.2em}}
\newcommand{\erase}[1]{\llbracket #1 \rrbracket}

@@

  \subsection{Equality and Reduction} \label{reduction}
  The operational semantics, and definitional $\beta$-equality of CLC is defined reductions as presented in Figure \ref{parallel}, all of which are entirely standard.
  \begin{figure}[H]
    \caption{Equality and Parallel Reduction}
    \begin{mathpar}
      \inferrule
      { m_1 \step^* n \\ m_2 \step^* n }
      { m_1 \equiv m_2 : A }
      \rname{Join}

      \inferrule
      {  }
      { (\lambda x.m)\ n \pstep m[n/x] }
      \rname{P-$\beta$}

      \inferrule
      { m \step m' }
      { \lambda x.m \step \lambda x.m' }
      \rname{Step-$\lambda$}

      \inferrule
      { A \pstep A' }
      { (x : A) \arw{s}{t} B \pstep (x : A') \arw{s}{t} B }
      \rname{Step-ProdL}

      \inferrule
      { B \pstep B' }
      { (x : A) \arw{s}{t} B \pstep (x : A) \arw{s}{t} B' }
      \rname{Step-ProdR}

      \inferrule
      { m \step m' }
      { m\ n \step m'\ n }
      \rname{Step-AppL}

      \inferrule
      { n \step n' }
      { m\ n \step m\ n' }
      \rname{Step-AppR}
    \end{mathpar}
    \label{parallel}
  \end{figure}
  As we have discussed previously, the elimination of the explicit ! exponential allows CLC to maintain a simple operational semantics, whose $\beta$-reductions are very well behaved.

@@

  \begin{lemma} Parallel reduction satisfies the diamond property. \\
    If $m \pstep_p m_1$ and $m \pstep_p m_2$ then there exists $m'$ such that $m_1 \pstep_p m'$ and $m_2 \pstep_p m'$.
  \end{lemma}

  \begin{corollary} The transitive reflexive closure of  reduction is confluent. \\ 
    If $m \step^* m_1$ and $m \step^* m_2$ then there exists $m'$ such that $m_1 \pstep^* m'$ and $m_2 \pstep^* m'$.
  \end{corollary}

@@

  \begin{lemma} Weakening. \\
    If $\Gamma \vdash m \stype{s} A$ is a valid judgment, then for any $x \notin \Gamma$, judgment $\Gamma, x \utype B \vdash m \stype{s} A$ is derivable.
  \end{lemma}
